A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-04-15 paper/paper.tex
misc stuff

\begin{figure}
    \begin{center}
    \includegraphics[width=0.9\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: Change diameter labels to $1, H, 2, J, 3, 2H, 4, 2J$ and put these on horizontal axis. TO DO: Change graph to show separate data points for each topological type. }
    \end{center}
    \label{global_statistics}
\end{figure}

@@

TO DO: Give a brief description of the algorithm used.

@@

TO DO: Discuss the big picture stuff concerning adding possible PL paths between vertices. Mention the benefits of hops and jumps not mentioned here (unique continuation of minimal paths)

We should mention another notable advantage of expanding the space of paths to include hops and edges. In classical differential geometry, the starting point, the initial direction, and length completely determine a geodesic. There is no branching of geodesics. This property of fundamental importance to many proofs in Riemannian geometry. If we use only edge-paths, then in a positively curved combinatorial 3-manifold it is possible to have two minimal paths with the same length and which begin by traversing the same edge, yet reach distinct destination vertices. That is, using only edge paths, minimal geodesics can ``branch''.

>>>>

\begin{figure}
    \begin{center}
    \includegraphics[width=0.9\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: CHANGE DIAMETER LABELS TO $1, H, 2, J, 3, 2H, 4, 2J$ AND PUT THESE ON HORIZONTAL AXIS. TO DO: CHANGE GRAPH TO SHOW SEPARATE DATA POINTS FOR EACH TOPOLOGICAL TYPE. TO DO: CREATE ANOTHER GRAPH WITH JUST EDGE DIAMETER COUNTS, WHERE THE CORRESPONDENCE BETWEEN DIAMETER(s) AND EDGE-DIAMETER IS $0\rightarrow 0, 1\rightarrow 1, \{H, 2\}\rightarrow 2, \{J,3\}\rightarrow 3, 4\rightarrow 4, 2J\rightarrow 5$}
    \end{center}
    \label{global_statistics}
\end{figure}

@@

TO DO: BRIEF DISCUSSION OF ALGORITHM USED

@@

TO DO: BIG PICTURE STUFF ABOUT EXTENDIND EDGE PATHS. WHY DOES IT HELP? CAN WE USE IT TO DO OTHER NICE THINGS? INCORPORATE FOLLOWING STUFF INTO DISCUSSION ...

We should mention another notable advantage of expanding the space of paths to include hops and edges. In classical differential geometry, the starting point, the initial direction, and length completely determine a geodesic. There is no branching of geodesics. This property of fundamental importance to many proofs in Riemannian geometry. If we use only edge-paths, then in a positi`vely curved combinatorial 3-manifold it is possible to have two minimal paths with the same length and which begin by traversing the same edge, yet reach distinct destination vertices. That is, using only edge paths, minimal geodesics can ``branch''.
